Fail Faster

### 2025-03-16 paper/paper.tex
minor

  % in strict functionallanguages like OCaml and Scal
To answer this, we propose a two-pronged approach for designing generator libraries 
that preserves their expressiveness while eliminating unnecessary overhead.
First, we describe a method of optimizing
generator libraries using \textit{staged metaprogramming}, or ``staging'', which has 
long been used for opetimizing idiomatic functional DSLs \todo{CITE!!!}.
We extend this technique to generators, completely eliminating the overhead of many common generator abstractions. For example, in unstaged generator libraries, each call to monadic bind constructs and immediately executes a closure at runtime.
Meanwhile, a staged approach can resolve the bind at compile time, enabling the compiler to inline and eliminate these closures.
Secondly, we demonstrate the
impact of different choices of \rand on generator performance 
by conducting a controlled comparison. Together, these insights provide a
recipe for improving even state-of-the-art generator libraries.

>>>>

  % in strict functionallanguages like OCaml and Scal
To answer this, we propose a two-pronged approach for designing generator libraries 
that preserves their expressiveness while eliminating unnecessary overhead.
First, we describe a method of optimizing
generator libraries using \textit{staged metaprogramming}, or ``staging'', which has 
long been used for optimizing idiomatic functional DSLs \todo{CITE!!!}.
We extend this technique to generators, completely eliminating the overhead of many common generator abstractions. For example, in unstaged generator libraries, each call to monadic bind constructs and immediately executes a closure at runtime.
Meanwhile, a staged approach can resolve the bind at compile time, enabling the compiler to inline and eliminate these closures.
Secondly, we demonstrate the
impact of different choices of \rand on generator performance 
by conducting a controlled comparison. Together, these insights provide a
recipe for improving even state-of-the-art generator libraries.
